[DRAFT] - Stage Oriented Design of an Intersection Management System Based on Laser Scanner Data

### 2016-11-08 paper01/paper.tex
Abstract modified in paper, added bg_process.eps

\begin{abstract}
In this work is described a stage-oriented design of an intersection management system based on a laser scanner sensor. After an introduction of the use of laser scanners in traffic monitoring, four stages are defined in the process flow of such a systems: preprocessing, feature analysis, pattern recognition and situation assesment. Then, an example implementation using a laser scanner dataset is presented.
\end{abstract}

>>>>

\begin{abstract}
The supervision of vehicular intersections is a major need for improving transportation systems because intersections are complex scenarios where different traffic actors interact between them. Recently, laser-based systems have been proposed and implemented to sense and to monitor intersections, giving good results as those based on cameras. In this work a stage-oriented design of an intersection management system based on laser scanner sensor data is proposed. The main objective of the proposed architecture is that it should have scalability, modularity, and high integrability. In order to achieve those objectives, the process flow of an intersection management system (IMS) is divided into four stages: preprocessing, feature analysis, pattern recognition, and situation assessment. Each of these stages is explained and some commonly used techniques are described. Finally, we present an example implementation using a laser scanner dataset, and a comparison between a single-laser approach and a multi-laser approach.

\end{abstract}
